### 2017-11-20 manuscript.rmd
corrected typos, updated character driven rotate. Knits

#Load tree
tree = species_tree_unladder
tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))
tree<-rotateNodes(tree,nodes=c(28,31))
#tree<-rotateNodes(tree,nodes=c(ape::mrca(tree)["Apolemia lanosa", "Agalma elegans"], ape::mrca(tree)["Abylopsis tetragona", "Hippopodius hippopus"]))
ultratree <- chronos(tree)
class( ultratree ) = "phylo"

@@

######VARS data barplot code
```{r vars_plot, echo=F, message=F, warning=F}
#Get Raw Data
raw_data = read.csv(file="characer_coding/trim_siphdepths.tsv", sep = "\t")[,c(4,3,5:11)]
raw_data = raw_data[order(raw_data$ConceptName),]

>>>>

#Load tree
tree = species_tree_unladder
tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))
#tree<-rotateNodes(tree,nodes=c(28,31))
tree<-rotateNodes(tree,nodes=ape::mrca(tree)["Agalma elegans","Hippopodius hippopus"])

ultratree <- chronos(tree)
class( ultratree ) = "phylo"

@@

######VARS data barplot code
```{r vars_plot, echo=F, message=F, warning=F}
#Get Raw Data
raw_data = read.csv(file="character_coding/trim_siphdepths.tsv", sep = "\t")[,c(4,3,5:11)]
raw_data = raw_data[order(raw_data$ConceptName),]
